Methodology for Assessing the State of the Practice for Domain X

### 2020-09-20 StateOfPractice/Methodology/Methodology.tex
updated section 5 of Methodology doc

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
The candidate software can be found through search engine queries and domain related publications. The candidate software should have the following properties:
\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather emprical measures found in Section \ref{SecEmpiricalMeasures}.
	\item \ad{``Ideally have the latest release or source code commit within the last 5 years.'' How about this one? Do we care about the ``vintage'' software?}
\end{enumerate}

>>>>

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
The candidate software can be found through search engine queries targeting authoritative lists of software from the domain, such as lists on GitHub and swMATH, and through searching domain related publications. Domain experts are also asked for their suggestions and are asked to review the list. The candidate software should have the following properties:

\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather empirical measures found in Section \ref{SecEmpiricalMeasures}.
	\item \ad{``Ideally have the latest release or source code commit within the last 5 years.'' How about this one? Do we care about the ``vintage'' software?}\pmi{I tested some software that has not been updated in about 8 years, as this software was mentioned in multiple places and looked professional. That being said, age should be noted as something that is considered along with other qualities. "Ideally the latest release or source code commit should be relatively recent, such as within the last 5 years, unless the candidate software appears to be well recommended and currently in use."}
\end{enumerate}
